Scattering of massless particles: scalars, gluons and gravitons

### 2024-07-03 test/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[CHY formula]{Scattering of massless particles: scalars, gluons and gravitons}
\subtitle{Freddy Cachazo, Song He, Ellis Ye Yuan}
\author{Su Yingze}
\institute{Nagoya University}
\date[7 23rd 2024]{July 23rd 2024} 
\begin{document}
\frame{\titlepage}

@@

here we ommit the coupling constant g, and $A_n^{tree}$ is called tree-level color-ordered partial amplitude.
Notice that this basis includes \textcolor{red}{$(n-1)!$} independent amplitudes.
\end{frame}
\begin{frame}
    Color-ordered partial amplitudes satisfy a set of well-known properties,
    \begin{itemize}
        \item Cyclic:\quad $$A_n^{tree}[1,2,3,\dots,n]=A_n^{tree}[2,3,\dots,n,1]$$
        \item Reflection: \quad $$A_n^{tree}[1,2,3,\dots,n]=(-1)^nA_n^{tree}[n,\dots,3,2,1]$$
        \item "photon" decoupling: \quad $$\sum_{\sigma\in \text{cyclic}}A_n^{tree}[1,\sigma(2,3,\dots,n)]=0$$
        \item KK(Kleiss-Kuijf) relation:\quad $$A_n^{tree}[1,{\alpha},n,{\beta}]=(-1)^{n_\beta}
        \sum_{\left\{\sigma\right\}_i\in OP(\left\{\alpha\right\},\left\{\beta\right\}^T)}A_n^{tree}[1,\left\{\sigma\right\}_i,n]$$
    \end{itemize}
    where the OP means ordered permutaions, that is all permutations of$\left\{\alpha\right\},\left\{\beta\right\}^T$
    that matains the order of individual elements of each set.
\end{frame}
\begin{frame}
    For example, a five point amplitude $A_n^{tree}(1,\{2,3\},5,\{4\})$, we have
\begin{equation*}
    A_n^{tree}[1,2,3,5,4]=-A_n^{tree}[1,2,3,4,5]-A_n^{tree}[1,2,4,3,5]-A_n^{tree}[1,4,2,3,5]
\end{equation*}
The other five point relations can be obtained by permuting legs 2,3,4 and using cyclic and reflection properties.
\\ \hspace*{\fill}\\
This means that the six amplitudes $A_n^{tree}(1,\mathcal{P}\{2,3,4 \},5 )$ form a basis of remaining five-point partial amplitudes.
\textcolor{red}{More generally, for multiplicity n, the KK relation can be used to rewrite any color-ordered partial amplitude in terms of only $(n-2)!$
basis partial amplitudes, where two legs are fixed(usually choose 1 and n).}
\end{frame}
\begin{frame}{A Similar Structure}
    It can be proved that tree level amplitudes can also be decomposed like 
\begin{equation*}
    \mathcal{A}_n^\text{tree}=\sum_{\sigma\in S_{n-2}}\tilde{f}^{a_1a_{\sigma_1}b_1}\tilde{f}^{b_1a_{\sigma_2}b_2}\cdots\tilde{f}^{b_{n-3}a_{\sigma_{n-2}}a_n}\tilde{A}_n(1,\sigma_1,\sigma_2,\ldots,\sigma_{n-2},n)
\end{equation*}
It is easy to realize that the number of basis amplitudes is also \textcolor{red}{$(n-2)!$}.
\end{frame}
\begin{frame}
    \begin{Large}
        \textcolor{red}{How can we realize the existence of this basis?}
    \end{Large}
\\ \hspace*{\fill}\\
We just need to notice the contribution from ladder diagram
\begin{figure}[htb]
    \centering
    \includegraphics[width=1\linewidth]{1.png}
\end{figure}
And any (three vertex) diagram, by using the Jacobbi identity like 
\begin{figure}[htb]
    \centering
    \includegraphics[width=1\linewidth]{2.png}
\end{figure}
can be transformed to the ladder diagram. It has been proved that $\textcolor{red}{\tilde{A}_n(\dots)}$ here is identical to $\textcolor{red}{A_n^{tree}[\dots]}$ in the trace basis.
\end{frame}
\begin{frame}{Color-Kinematics Duality and BCJ Relation}
The Color-Kinematics Duality here is not the complete version, but we can sketch some point from lower point case
\end{frame}

@@

        s=0\quad\to \quad \text{a corresponding sclar theory}

@@

    The conclusion of the factors above

@@

        \mathcal{C}_{U(N)}\equiv \left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)\quad \mathrm{and} \quad E_\epsilon\equiv\mathrm{Pf}^{'}\Psi(\epsilon)

@@

@@

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usepackage{tikz}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[CHY formula]{Scattering of massless particles: scalars, gluons and gravitons}
\subtitle{Freddy Cachazo, Song He, Ellis Ye Yuan}
\author{Su Yingze}
\institute{Nagoya University}
\date[7 23rd 2024]{July 23rd 2024} 
\begin{document}
\frame{\titlepage}

@@

here we ommit the coupling constant g, and $A_n^{tree}$ is called tree-level color-ordered partial amplitude.
Notice that this basis includes \textcolor{red}{$(n-1)!$} independent amplitudes.
\end{frame}
\begin{frame}
    Color-ordered partial amplitudes satisfy a set of well-known properties,
    \begin{itemize}
        \item Cyclic:\quad $$A_n^{tree}[1,2,3,\dots,n]=A_n^{tree}[2,3,\dots,n,1]$$
        \item Reflection: \quad $$A_n^{tree}[1,2,3,\dots,n]=(-1)^nA_n^{tree}[n,\dots,3,2,1]$$
        \item "photon" decoupling: \quad $$\sum_{\sigma\in \text{cyclic}}A_n^{tree}[1,\sigma(2,3,\dots,n)]=0$$
        \item KK(Kleiss-Kuijf) relation:\quad $$A_n^{tree}[1,{\alpha},n,{\beta}]=(-1)^{n_\beta}
        \sum_{\left\{\sigma\right\}_i\in OP(\left\{\alpha\right\},\left\{\beta\right\}^T)}A_n^{tree}[1,\left\{\sigma\right\}_i,n]$$
    \end{itemize}
    where the OP means ordered permutaions, that is all permutations of$\left\{\alpha\right\},\left\{\beta\right\}^T$
    that matains the order of individual elements of each set.
\end{frame}
\begin{frame}
    For example, a five point amplitude $A_n^{tree}(1,\{2,3\},5,\{4\})$, we have
\begin{equation*}
    A_n^{tree}[1,2,3,5,4]=-A_n^{tree}[1,2,3,4,5]-A_n^{tree}[1,2,4,3,5]-A_n^{tree}[1,4,2,3,5]
\end{equation*}
The other five point relations can be obtained by permuting legs 2,3,4 and using cyclic and reflection properties.
\\ \hspace*{\fill}\\
This means that the six amplitudes $A_n^{tree}(1,\mathcal{P}\{2,3,4 \},5 )$ form a basis of remaining five-point partial amplitudes.
\textcolor{red}{More generally, for multiplicity n, the KK relation can be used to rewrite any color-ordered partial amplitude in terms of only $(n-2)!$
basis partial amplitudes, where two legs are fixed(usually choose 1 and n).}
\end{frame}
\begin{frame}{A Similar Structure}
    It can be proved that tree level amplitudes can also be decomposed like 
\begin{equation*}
    \mathcal{A}_n^\text{tree}=\sum_{\sigma\in S_{n-2}}\tilde{f}^{a_1a_{\sigma_1}b_1}\tilde{f}^{b_1a_{\sigma_2}b_2}\cdots\tilde{f}^{b_{n-3}a_{\sigma_{n-2}}a_n}\tilde{A}_n(1,\sigma_1,\sigma_2,\ldots,\sigma_{n-2},n)
\end{equation*}
The basis is called DDM and more convenient in parctice. It is easy to realize that the number of basis amplitudes is also \textcolor{red}{$(n-2)!$} with fiexed particle labels 1 and n.
\end{frame}
\begin{frame}
    \begin{Large}
        \textcolor{red}{How can we realize the existence of this basis?}
    \end{Large}
\\ \hspace*{\fill}\\
We just need to notice the contribution from ladder diagram
\begin{figure}[htb]
    \centering
    \includegraphics[width=1\linewidth]{1.png}
\end{figure}
And any (three vertex) diagram, by using the Jacobbi identity like 
\begin{figure}[htb]
    \centering
    \includegraphics[width=1\linewidth]{2.png}
\end{figure}
can be transformed to the ladder diagram. It has been proved that $\textcolor{red}{\tilde{A}_n(\dots)}$ here is identical to $\textcolor{red}{A_n^{tree}[\dots]}$ in the trace basis.
\end{frame}
\begin{frame}{Color-Kinematics Duality and BCJ Relation}
The Color-Kinematics Duality here is not the complete version, but we can sketch some point from lower point case
\end{frame}

@@

        s=0\quad\to \quad \text{a corresponding scalar theory}

@@

    All of above leads to the conclusion that the factors 

@@

        \mathcal{C}_{U(N)}\equiv \sum_{\sigma\in S_n/Z_n}\left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)\quad \mathrm{and} \quad E_\epsilon\equiv\mathrm{Pf}^{'}\Psi(\epsilon)

@@

    are interchangeable and this is a color-Kinematics corresopondence which is valid for individual solutions to scattering equations.

@@

\begin{frame}
    The connection of amplitudes between 3 theories can be described by the following diagram 
    \begin{figure}[htb]
        \centering
        \includegraphics[width=1\linewidth]{main.png}
    \end{figure}
\end{frame}
\begin{frame}
    \frametitle{Double partial amplitudes}
    Because there are two color indices in this sclar theory, so it can be anticipateed that the amplitude
    have double trace decomposition structure
    \begin{align*}
        \mathcal{M}_n^{(0)}&=\sum_{\alpha\in S_n/Z_n}\mathrm{Tr}(\tilde{T}^{\mathsf{b}_{\alpha(1)}}\tilde{T}^{\mathsf{b}_{\alpha(2)}}\cdots\tilde{T}^{\mathsf{b}_{\alpha(n)}})M_n^{(0)}(\alpha(1),\alpha(2),\ldots,\alpha(n))\\
        &=\sum_{\alpha,\beta\in S_n/Z_n}\mathrm{Tr}(\tilde{T}^{\mathsf{b}_{\alpha(1)}}\tilde{T}^{\mathsf{b}_{\alpha(2)}}\cdots\tilde{T}^{\mathsf{b}_{\alpha(n)}})\text{Tr}(T^{\mathtt{a}_{\beta(1)}}T^{\mathtt{a}_{\beta(2)}}\cdots T^{\mathtt{a}_{\beta(n)}})\\
        &\times \alert{m_n^{(0)}(\alpha|\beta)}
    \end{align*} 
    where the last term $m_n^{(0)}(\alpha|\beta)$ is called \alert{double partial amplitude} and can be read off from the full amplitude
    \begin{align*}
    m_{n}^{(0)}(\alpha|\beta)&=\int\frac{d^{n}\sigma}{\operatorname{vol}\operatorname{SL}(2,\mathbb{C})}\frac{\prod_{a}{}^{\prime}\delta(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}})}{(\sigma_{\alpha(1),\alpha(2)}\cdots\sigma_{\alpha(n),\alpha(1)})(\sigma_{\beta(1),\beta(2)}\cdots\sigma_{\beta(n),\beta(1)})}\\
    =&\sum_{\{\sigma\}\in\mathrm{solutions}}\frac1{\det^{\prime}\Phi}\frac{1}{(\sigma_{\alpha(1),\alpha(2)}\cdots\sigma_{\alpha(n),\alpha(1)})(\sigma_{\beta(1),\beta(2)}\cdots\sigma_{\beta(n),\beta(1)})}
    \end{align*}

\end{frame}
\begin{frame}
    Likewise the decomposition in the first section, it is more usually to write the amplitudes in terms of colore basis
    \begin{equation*}
        \boxed{\mathbf{c}_\alpha\equiv\sum_{\mathsf{c}_1,...,\mathsf{c}_{n-3}}f_{\mathsf{a}_1\mathsf{a}_{\alpha(2)}\mathsf{c}_1}\cdots f_{\mathsf{c}_{n-3}\mathsf{a}_{\alpha(n-1)}\mathsf{a}_n}}
    \end{equation*}
    where $\alpha \in S_{n-2}$. The amplitude is 
    \begin{equation*}
        \mathcal{M}_n^{(0)}=\sum_{\alpha,\beta\in S_{n-2}}\mathbf{c_\alpha}\tilde{\mathbf{c_\beta}}m_{n}^{(0)}(\alpha|\beta)
    \end{equation*}
\end{frame}
\begin{frame}
    \frametitle{Examples}
    \begin{itemize}
        \item The simplest example is the 3 point case
        \begin{equation*}
            \mathcal{M}_3^{(0)}(1^{aa^\prime,bb^\prime,cc^\prime})=(\sigma_{12}\sigma_{23}\sigma_{31})^2\frac{f_{abc}f_{a^\prime b^\prime c^\prime}}{(\sigma_{12}\sigma_{23}\sigma_{31})^2}=f_{abc}f_{a^\prime b^\prime c^\prime}
        \end{equation*}
        It actually gives the correct answer.
        \item The 4 point case is a little complex. Solving the scattering equations with $\sigma_1=0,\sigma_2=1,\sigma_3=\infty$ gives $\sigma_4=-s_{23}/s_{12}$. Define
        $s_{12}=s$, $s_{23}=t$, $s_{13}=u$, the color factors are 
        \begin{equation*}
            \mathbf{c_s}=\sum_bf_{a_1a_2b}f_{ba_3a_4},\mathbf{c_t}=\sum_bf_{a_1a_4b}f_{ba_3a_2},\mathbf{c_u}=\sum_bf_{a_1a_3b}f_{ba_2a_4}
        \end{equation*}
        Denoting the ordering $(1324)$ as $P$ and comuputing $\det{'}\Phi=\frac{s^2}{t}/(\sigma_{12}\sigma_{23}^2\sigma_{31}\sigma_{34}\sigma_{42})$, one gets
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{align*}
        \!\!\!\!\mathcal{M}_4^{(0)}&=\mathbf{c_s}\tilde{\mathbf{c_s}}m_4^{(0)}(I;I)+\mathbf{c_s}\tilde{\mathbf{c_u}}m_4^{(0)}(I;P)+\mathbf{c_u}\tilde{\mathbf{c_s}}m_4^{(0)}(P;I)+\mathbf{c_u}\tilde{\mathbf{c_u}}m_4^{(0)}(P;P)\\
        &=\mathbf{c_s}\tilde{\mathbf{c_s}}\frac{u}{st}+(\mathbf{c_s}\tilde{\mathbf{c_u}}+\mathbf{c_u}\tilde{\mathbf{c_s}})\frac{1}{t}+\mathbf{c_u}\tilde{\mathbf{c_u}}\frac{s}{ut}\\
        &=-\frac{\mathbf{c_s}\tilde{\mathbf{c_s}}}{s}-\frac{\mathbf{c_t}\tilde{\mathbf{c_t}}}{t}-\frac{\mathbf{c_u}\tilde{\mathbf{c_u}}}{u}
    \end{align*}
    \quad \quad as expected for a color-dressed cubic theory.
    \begin{itemize}
        \item For the five point, I just give the results of some double partial amplitudes.
        Denoting the orderings as $I=P_0$, $(13245)=P_1$, $(12435)=P_2$, $(14325)=P_3$, $(13425)=P_4$, $(14235)=P_5$
        \begin{equation*}
            \begin{aligned}&m_5^{(0)}(I|I)=\frac{1}{s_{12}s_{34}}+\frac{1}{s_{23}s_{45}}+\frac{1}{s_{34}s_{51}}+\frac{1}{s_{45}s_{12}}+\frac{1}{s_{51}s_{23}},\\&m_5^{(0)}(I|P_1)=-\frac{1}{s_{23}}\left(\frac{1}{s_{45}}+\frac{1}{s_{12}}\right),\quad
                m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}}\left(\frac{1}{s_{51}}+\frac{1}{s_{12}}\right).\end{aligned}
        \end{equation*}
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{align*}
        &m_5^{(0)}(I|P_3)=-\frac{1}{s_{51}}\left(\frac{1}{s_{23}}+\frac{1}{s_{34}}\right),\quad  m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}s_{51}},\\
        &m_5^{(0)}(I|P_5)=0
    \end{align*}
\end{frame}
